---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# blue 

<!-- badges: start -->
[![R-CMD-check](https://github.com/Helenzzz07/blue/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Helenzzz07/blue/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/Helenzzz07/blue/graph/badge.svg)](https://app.codecov.io/gh/Helenzzz07/blue)
<!-- badges: end -->

The blue package provides a simple R interface for exploring track and field results from the Paris 2024 Olympic Games.
It is distinct from other packages because it includes 2024 athlete-level data and supports flexible filtering and plotting.

  
## Installation

You can install the development version of blue from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("Helenzzz07/blue")
```



## Example

This is a basic example that shows how to look up and visualize top 10 athlete’s performance:
 
```{r}
library(blue)
library(dplyr)

# Find the results URL for a specific athlete
find_athlete("Álvaro MARTÍN")

# Plot the top 10 athletes's performance in final round
plot_event_top10 ("20 Kilometres Race Walk")
```

```{r}
# Warning: Athlete not found.
plot_event_top10("Fake Athlete")
```

    
    
    
    
    
    
      
    
    
    
    
    
   
